---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE, fig.retina=2, message=FALSE, warning=FALSE)
options(width=120)
```

[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/cspy.svg?branch=master)](https://travis-ci.org/hrbrmstr/cspy) 
[![Coverage Status](https://codecov.io/gh/hrbrmstr/cspy/branch/master/graph/badge.svg)](https://codecov.io/gh/hrbrmstr/cspy)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/cspy)](https://cran.r-project.org/package=cspy)

# cspy

Content Security Policy Decomposer & Evaluator

## Description

Methods are provided to decompose, display, and validate
content security policy header values. Wraps the 'Shape Security'
'salvation' Java library (<https://github.com/shapesecurity/salvation>).
Package version tracks 'salvation' Java archive version.

## What's Inside The Tin

The following functions are implemented:

Core:

- `fetch_csp`:	Fetch and/or parse a content security policy header value
- `has_csp`:	Does a URL have a content security policy?
- `parse_csp`:	Fetch and/or parse a content security policy header value
- `validate_csp`:	Validate a CSP
- `as.data.frame.csp`:	Convert a parsed CSP into a data frame of directives and values

Security/Safety Checks:

- `check_deprecated`:	Tests for insecure CSP settings
- `check_ip_source`:	Tests for insecure CSP settings
- `check_missing_directives`:	Tests for insecure CSP settings
- `check_nonce_length`:	Tests for insecure CSP settings
- `check_plain_url_schemes`:	Tests for insecure CSP settings
- `check_script_unsafe_eval`:	Tests for insecure CSP settings
- `check_script_unsafe_inline`:	Tests for insecure CSP settings
- `check_src_http`:	Tests for insecure CSP settings
- `check_wildcards`:	Tests for insecure CSP settings

Testers:

- `allows_child_from_source`:	Tests for what a parsed CSP allows
- `allows_connect_to`:	Tests for what a parsed CSP allows
- `allows_font_from_source`:	Tests for what a parsed CSP allows
- `allows_form_action`:	Tests for what a parsed CSP allows
- `allows_frame_ancestor`:	Tests for what a parsed CSP allows
- `allows_frame_from_source`:	Tests for what a parsed CSP allows
- `allows_manifest_from_source`:	Tests for what a parsed CSP allows
- `allows_media_from_source`:	Tests for what a parsed CSP allows
- `allows_navigation`:	Tests for what a parsed CSP allows
- `allows_object_from_source`:	Tests for what a parsed CSP allows
- `allows_prefetch_from_source`:	Tests for what a parsed CSP allows
- `allows_script_from_source`:	Tests for what a parsed CSP allows
- `allows_script_with_nonce`:	Tests for what a parsed CSP allows
- `allows_style_from_source`:	Tests for what a parsed CSP allows
- `allows_style_with_nonce`:	Tests for what a parsed CSP allows
- `allows_unsafe_inline_script`:	Tests for what a parsed CSP allows
- `allows_unsafe_inline_style`:	Tests for what a parsed CSP allows
- `allows_worker_from_source`:	Tests for what a parsed CSP allows

## Installation

```{r install-ex, eval=FALSE}
install.packages("cspy", repos = "https://cinc.rud.is/")
```

## Usage

```{r lib-ex}
library(cspy)
library(tibble) # for printing

# current version
packageVersion("cspy")

```

```{r one}
has_csp("https://community.rstudio.com")

csp <- fetch_csp("https://community.rstudio.com")

csp

(csp_df <- as.data.frame(csp))

allows_unsafe_inline_script(csp)

check_deprecated(csp_df)

check_ip_source(csp_df)

check_missing_directives(csp_df)

check_nonce_length(csp_df)

check_plain_url_schemes(csp_df)

check_script_unsafe_eval(csp_df)

check_script_unsafe_inline(csp_df)

check_src_http(csp_df)

check_wildcards(csp_df)
```

## crsspy Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). 
By participating in this project you agree to abide by its terms.
